Job Demands-Resources model components through the lens of O*NET classifications

### 2023-02-04 Submission.Rmd
ANOVA results added to body of paper (prior to Discussion section)

ADD THIS!

@@

rstatix::anova_test(data=overwork,dv=score,wid=subject,within=type)

## trying to replicate - doesn't work 1/31/23

trying <- aov(formula = score ~ type + Error(subject/type), data=overwork)
summary(trying)

@@

## pairwise_t_test( value~time,paired=TRUE, p.adjust.method = "bonferroni" )

# check <- overwork[,c(406:407)]
# psych::describe.by(check, group=check$type)

@@

>>>>

Table \@ref(tab:cortab) highlights hypothesis 2. A large number of correlations are moderate. Challenge and hindrance demands are smaller in relationship but mostly negative. Challenge and resource are typically large. Only some are small (for example information input and physical challenges). For the most part there are strong associations between challenges and resources.

@@

phyenvir <- anova1[ which(anova1$type=='resources_phyenvironment' | anova1$type=='challenge_phyenvironment' | anova1$type=='hindrance_phyenvironment'), ]

timepress <- anova1[ which(anova1$type=='resources_timepressure' | anova1$type=='challenge_timepressure' | anova1$type=='hindrance_timepressure'), ]

emodemand <- anova1[ which(anova1$type=='resources_emotionaldemands' | anova1$type=='challenge_emotionaldemands' | anova1$type=='hindrance_emotionaldemands'), ]

recipcon <- anova1[ which(anova1$type=='resources_recipientcontact' | anova1$type=='challenge_recipientcontact' | anova1$type=='hindrance_recipientcontact'), ]

workpress <- anova1[ which(anova1$type=='resources_workpressure' | anova1$type=='challenge_workpressure' | anova1$type=='hindrance_workpressure'), ]

report1 <- rstatix::anova_test(data=overwork,dv=score,wid=subject,within=type, effect.size="pes") 
report2 <- rstatix::anova_test(data=phyenvir,dv=score,wid=subject,within=type, effect.size="pes") 
report3 <- rstatix::anova_test(data=timepress,dv=score,wid=subject,within=type, effect.size="pes") 
report4 <- rstatix::anova_test(data=emodemand,dv=score,wid=subject,within=type, effect.size="pes") 
report5 <- rstatix::anova_test(data=recipcon,dv=score,wid=subject,within=type, effect.size="pes") 
report6 <- rstatix::anova_test(data=workpress,dv=score,wid=subject,within=type, effect.size="pes")

@@

@@

The effect for `Overwork` was `r report1$ANOVA$F`, partial eta squared was `r report1$ANOVA$pes`
The effect for `Physical Environment` was `r report2$ANOVA$F`, partial eta squared was `r report2$ANOVA$pes`
The effect for `Time Pressure` was `r report3$ANOVA$F`, partial eta squared was `r report3$ANOVA$pes`
The effect for `Emotional Demands` was `r report4$ANOVA$F`, partial eta squared was `r report4$ANOVA$pes`
The effect for `Recipient Contact` was `r report5$ANOVA$F`, partial eta squared was `r report5$ANOVA$pes`
The effect for `Work Pressure` was `r report6$ANOVA$F`, partial eta squared was `r report6$ANOVA$pes`

### 2023-02-04 Submission.tex
ANOVA results added to body of paper (prior to Discussion section)

ADD THIS!

@@

\begin{verbatim}
## ANOVA Table (type III tests)
## 
## $ANOVA
##   Effect DFn  DFd      F        p p<.05   ges
## 1   type   2 1134 17.709 2.67e-08     * 0.017
## 
## $`Mauchly's Test for Sphericity`
##   Effect     W        p p<.05
## 1   type 0.694 1.29e-45     *
## 
## $`Sphericity Corrections`
##   Effect   GGe       DF[GG]    p[GG] p[GG]<.05   HFe      DF[HF]    p[HF]
## 1   type 0.766 1.53, 868.32 7.09e-07         * 0.767 1.53, 870.2 6.93e-07
##   p[HF]<.05
## 1         *
\end{verbatim}

\begin{verbatim}
## 
## Error: subject
##           Df Sum Sq Mean Sq F value Pr(>F)
## Residuals  1  8.266   8.266               
## 
## Error: subject:type
##      Df Sum Sq Mean Sq
## type  2  15.04   7.519
## 
## Error: Within
##             Df Sum Sq Mean Sq F value  Pr(>F)   
## type         2    9.2   4.586   5.989 0.00256 **
## Residuals 1698 1300.2   0.766                   
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

>>>>

Table \ref{tab:cortab} highlights hypothesis 2. A large number of correlations are moderate. Challenge and hindrance demands are smaller in relationship but mostly negative. Challenge and resource are typically large. Only some are small (for example information input and physical challenges). For the most part there are strong associations between challenges and resources.

@@

The effect for \texttt{Overwork} was 17.71, partial eta squared was 0.03
The effect for \texttt{Physical\ Environment} was 112.97, partial eta squared was 0.17
The effect for \texttt{Time\ Pressure} was 82.22, partial eta squared was 0.13
The effect for \texttt{Emotional\ Demands} was 393.43, partial eta squared was 0.42
The effect for \texttt{Recipient\ Contact} was 1,031.73, partial eta squared was 0.65
The effect for \texttt{Work\ Pressure} was 718.12, partial eta squared was 0.56
